---
title: "p8105_hw1_wz2590"
output: github_document
author: Weiheng Zhang
---



### Problem 1


```{r  problem 1-1, message = FALSE}
library(tidyverse)

set.seed(124) # set the random seed to make the results reproducible. 
              # I just like the number 124

## data frames
example_df = 
  tibble(
    n_distribution = rnorm(10),
    logical_vec = n_distribution > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("male", "male", "male", "female", "female", "female", 
                          "bisex", "bisex", "bisex", "bisex"))
  )

example_df
```

```{r problem 1-2, message = FALSE}
mean(example_df$n_distribution)
mean(example_df$logical_vec)
mean(example_df$char_vec)
mean(example_df$factor_vec)
```

Taking mean from the random normal distribution and the logical vector works.  
Taking mean from the character vector and the factor vector returned NA, because the elements in these vectors are neigher numeric nor logical (according to the warning messages).


This is the code chunk to apply as.numeric to the logical, character, and factor variables.
```{r  problem 1-3, warning = FALSE, results="hide"}
as.numeric(example_df$logical_vec)
as.numeric(example_df$char_vec)
as.numeric(example_df$factor_vec)
```

In the logical vector, TRUE is converted to 1 and FALSE is converted to 0. This is why taking mean of this vector can return a valid float number as the mean.  
  
While in the character vector, all elements are converted to NA. This is why taking mean of this vector will still return NA.  
  
The as.numeric function will convert elements in a factor vector to their corresponding levels. But it seems that directly call the "mean" function on a factor vector will not apply as.numeric automatically thus still returned NA as mean.  

### Problem 2
```{r  problem 2-1, message = FALSE}
data("penguins", package = "palmerpenguins")
penguins
```

This is a tibble dataset about penguins. Each penguin has the following characteristics: `r colnames(penguins)`  

The dimensions of this tibble: `r nrow(penguins)` * `r ncol(penguins)`. There are 344 penguins included, and each penguin has eight characteristics.

The mean flipper length in mm is: `r mean(penguins$flipper_length_mm, na.rm=TRUE)` mm


```{r  problem 2-2, warning = FALSE, message = FALSE}
plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
plot + labs(title = "Scatterplot of penguins' flipper_length vs bill_length in mm")
ggsave("P2_scatterplot.pdf", height = 4, width = 6)
```


